---
title: "All STPs"
author: "Philippine Chambault"
date: "12/17/2021"
output:
  bookdown::html_document2:
    number_sections: yes
    code_folding: show
    df_print: default
    fig_caption: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = TRUE,
  fig.align = "center",
  message = FALSE,
  warning = FALSE,
  # cache   = FALSE,
  out.width = "100%"
  # comment = NA
)
```

                       

```{r, global_options, include=FALSE}
library(ggplot2)
library(tidyquant)
library(gridExtra)
library(tidyverse)
library(dplyr)
library(viridis)
library(DT)
library(data.table)
Sys.setlocale("LC_TIME", "English")
```



# Import data {.tabset}

```{r, echo=TRUE}
setwd("/Users/philippinechambault/Documents/POST-DOC/2021/MSCA-GF/ANALYSES")
stp  <- readRDS("./Rdata/STP/stp_all_LR_with_type.RDS")
DT::datatable(stp[1:30,],options=list(scrollX=T))
stp = data.frame(stp)
# number of records
nrow(stp)
# number of individuals
length(unique(stp$ptt))
# number of ST start & end: more starts than end !
table(stp$type2)
# range values for STP: removed outliers < 10 and > 38 deg
summary(stp$stp)

# start and end date for each ID
dat = stp[,c("ptt","dateTime","stp")] %>%
    group_by(ptt) %>%
    summarise(start=head(dateTime,1),
              end=tail(dateTime,1),
              nrow=n())
dat$duration = difftime(dat$end, dat$start,units="days")

# number of records and ST drops/ID
feed = stp[,c("ptt","dateTime","stp","feed","type2")] %>%
  group_by(ptt,type2) %>%
  summarise(STdrop=n())
feed = feed[feed$type2=="start",]
dat  = merge(dat, feed[,c("ptt","STdrop")],by="ptt")

# number of daily ST drops/ID
dat$daily_drop = dat$STdrop / as.numeric(dat$duration)
dat = dat[order(dat$daily_drop),]
dat
```



# ST profile over time

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="ST profiles over time."}
ggplot(stp[!is.na(stp$stp),], aes(x=dateTime, y=stp)) +
  geom_point(size=0.2) + 
  geom_point(data=stp[stp$type2=="start",], colour="red",shape=15) +
  geom_path() +
  labs(x="", y="STP (degrees)") +
  facet_wrap(~ptt, scales="free_x") +
  theme_tq()
```



# Depth profile over time

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profiles over time."}
ggplot(stp[!is.na(stp$stp),], aes(x=dateTime, y=-depth)) +
  geom_point(aes(colour=stp)) + 
  labs(x="", y="Depth (m)") +
  facet_wrap(~ptt, scales="free") +
  scale_color_viridis() +
  theme_tq()
```

# Depth profile according to ST

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profiles according to ST."}
ggplot(stp[!is.na(stp$depth),], aes(x=stp, y=-depth, colour=ptt)) +
  geom_point() + 
  labs(x="ST (deg)", y="Depth (m)") +
  # geom_smooth(method="gam", aes(colour=ptt)) +
  scale_colour_tq() +
  theme_tq()
```


# STP duration

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profiles over time."}
ggplot(stp[!is.na(stp$stp),], aes(y=days, x=ptt, colour=ptt)) +
  geom_line(size=2) + 
  scale_y_continuous(name="Days", breaks=seq(1,max(stp$days,by=1))) +
  scale_color_tq() +
  coord_flip() +
  theme_tq() +
  theme(legend.position="none")
```


# Number of ST drops per individual

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the number of ST drops per individual."}
ggplot(dat, aes(y=STdrop, x=reorder(ptt,STdrop), fill=ptt)) +
  geom_bar(stat="identity") + # , position=position_dodge()
  labs(x="ID", y="Number of ST drops") +
  geom_text(aes(label=dat$STdrop), vjust=0, size=4) +
  scale_fill_tq() +
  theme_tq() +
  theme(legend.position="none")
```



# Number of daily ST drops per individual

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the number of daily ST drops per individual."}
ggplot(dat, aes(y=daily_drop, x=reorder(ptt,daily_drop), fill=ptt)) +
  geom_bar(stat="identity") + # , position=position_dodge()
  labs(x="ID", y="Number of daily ST drops") +
  geom_text(aes(label=round(dat$daily_drop)), vjust=0, size=4) +
  scale_fill_tq() +
  theme_tq() +
  theme(legend.position="none")
```




# Boxplot of ST during feeding vs no feeding

```{r, echo=TRUE}
stp$feed = factor(stp$feed, levels=c("no feeding","feeding"))

# average ST during feeding and no feeding
stp %>%
  group_by(ptt,feed) %>%
  summarize(mean=mean(stp,na.rm=T),
            sd=sd(stp,na.rm=T))
# kruskal Wallis test between feeding and no feeding
kruskal.test(stp$stp, stp$feed)

# number of ST events / ID
stp %>%
  group_by(ptt) %>%
  summarise(counts_nofeed=table(feed)[1],
            counts_feed=table(feed)[2])

# number of start and end / ID
stp %>%
  group_by(ptt) %>%
  summarise(counts_start=table(type2)[4],
            counts_end=table(type2)[1])
```
Something is wrong with the detection of feeding end; always less ends than starts.


```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the number of daily ST drops per individual."}
ggplot(stp, aes(y=stp, x=ptt, fill=feed)) +
  geom_boxplot() +  
  labs(x="ID", y="STP (deg)") +
  scale_fill_tq() +
  theme_tq() 
```

Lots of outliers for Frida, 7618-15 and Thora.




# Boxplot of depth during ST drops

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the number of daily ST drops per individual."}
ggplot(stp[!is.na(stp$depth),], aes(y=-depth, x=ptt, fill=ptt)) +
  geom_boxplot() + 
  labs(x="ID", y="STP (deg)") +
  scale_fill_tq() +
  theme_tq()  +
  theme(legend.position="none")
```
