---
title: "Visual match acousonde-STP for Eistla"
author: "Philippine CHAMBAULT"
date: "22/11/2021"
output:
  bookdown::html_document2:
    number_sections: yes
    code_folding: show
    df_print: default
    fig_caption: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = TRUE,
  fig.align = "center",
  message = FALSE,
  warning = FALSE,
  # cache   = FALSE,
  out.width = "100%"
  # comment = NA
)
```

                       

```{r, global_options, include=FALSE}
library(ggplot2)
library(ggbeeswarm)
library(raincloudplots)
library(PupillometryR)
library(gridExtra)
library(tidyverse)
library(dplyr)
library(viridis)
library(DT)
library(data.table)
Sys.setlocale("LC_TIME", "English")
```





# Import data {.tabset}

## STP 
```{r, echo=TRUE}
stp  <- readRDS("C:/Users/phili/Documents/POST-DOC/2021/MSCA-GF/ANALYSES/Rdata/STP/stp_eistla.RDS")
DT::datatable(stp[1:30,],options=list(scrollX=T))

# Duration of the STP
round(difftime(stp$dateTime[nrow(stp)], stp$dateTime[1], units="days")) 
```

## Acousonde
```{r, echo=TRUE}
buzz <- readRDS("C:/Users/phili/Documents/POST-DOC/2021/MSCA-GF/ANALYSES/Rdata/Acousonde/buzz_eistla_phases_2m.RDS")
DT::datatable(buzz[1:100,],options=list(scrollX=T)) 

# Time elapsed (in days) between release and first buzz:
round(difftime(buzz$dateTime[buzz$buzz==1][[1]], 
               buzz$dateTime[1], units="hours"))

# Duration of the acousonde
round(difftime(buzz$dateTime[nrow(buzz)], buzz$dateTime[1], units="days"))

# date after which stp is constant
head(stp$dateTime[stp$stp<32 & !is.na(stp$stp)],1)
```


# STP over time {.tabset}

## All data included
```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Stomach temperature over time and according to event type."}
ggplot(stp, aes(x=dateTime, y=stp)) +
  geom_path(size=0.2,shape=19) +
  geom_point(size=1.5, aes(colour=type)) +
  labs(x="", y="STP (deg)",title="Eistla") +
  geom_hline(yintercept=c(20,40),color="blue",linetype=4) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 
```
2 outliers above 38 and possibly 1 below 20 degrees, but only a few records. 
Let's remove these outliers and see what the curve looks like.

## Without outliers
```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Stomach temperature over time and according to event type."}
ggplot(stp[!(stp$stp>38 | stp$stp<20 | is.na(stp$stp)),], aes(x=dateTime, y=stp)) +
  geom_path(size=0.2,shape=19) +
  geom_point(size=1.5, aes(colour=type)) +
  ylim(25,38) +
  labs(x="", y="STP (deg)",title="Eistla") +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text  = element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 
```
After 2016-08-26 02:11:00, STP is constant. 



# Temporal overlap

```{r, echo=TRUE}
buzz$type2 = "Acousonde"
stp$type2  = "STP"
stp = data.frame(stp)
# stp = stp[!(stp$stp<10 | stp$stp>40),]
dat = rbind(buzz[,c("dateTime","type2")], 
            stp[!is.na(stp$depth),c("dateTime","type2")])
dat$type2 = as.factor(dat$type2)
buzz = data.frame(buzz)
b = buzz[buzz$buzz==1,]

# temporal overlap between STP and buzzes
t = stp[!is.na(stp$depth),]
round(difftime(t$dateTime[nrow(t)], 
               buzz$dateTime[buzz$buzz==1][[1]], units="hours")) 
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Temporal overlap between the STP and the acousonde. Red dots refer to buzzes."}
ggplot(dat, aes(y=dateTime, x=type2)) +
  geom_point(size=1.5,colour="black",shape=19) +
  geom_point(data=b,size=1.5,colour="red",shape=19) +
  labs(x="", y="Time",title="Eistla") +
  coord_flip() +
  geom_hline(data=b, aes(yintercept=as.numeric(dateTime[1])),
             color="blue",linetype=4) +
  geom_hline(aes(yintercept=as.numeric(t$dateTime[nrow(t)])), 
             color="blue",linetype=4) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 
```
Only 34 hours of overlap between the acousonde when buzzes and the STP.





# Correlation between STP and Acousonde 

```{r, echo=FALSE}
merge <- readRDS("C:/Users/phili/Documents/POST-DOC/2021/MSCA-GF/ANALYSES/Rdata/merge_depth_STP_Acousonde_Eistla.RDS")
merge = merge[!is.na(merge$depth.y),]
cor.test(merge$depth.y, merge$depth.x)
summary(merge$stp)
# number of ST records
nrow(merge)
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Correlation between depth recorded from STP and the ones from Acousonde."}
ggplot(merge, aes(depth.x, depth.y)) +
  labs(x="Depth from STP (m)",y="Depth from Acousonde (m)",title="Eistla") +
  geom_smooth(method=lm,size=0.6) +
  geom_point(size=3, colour="brown") + 
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 
```






# Visual inspection {.tabset}

## 25 August 06:30

```{r, echo=FALSE}
acou = setDT(buzz)[dateTime %between% c('2016-08-25 06:20:00',
                                        '2016-08-25 07:00:00')]
st = setDT(stp)[dateTime %between% c('2016-08-25 06:20:00', 
                                     '2016-08-25 07:00:00')]
st[!is.na(st$depth),c(1,5:6,8:11)]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profile on 25th August at 06:20 from the acousonde and depths recorded by the STP in green and buzzes in red."}
ggplot(acou, aes(dateTime, -depth)) +
  geom_path(size=0.1) + 
  geom_point(data=acou[acou$buzz==1,], size=1.5,colour="red",shape=15) +
  geom_point(size=2, data=st, aes(y=-depth, x=dateTime), colour="green") + 
  labs(x="", y="Depth (m)",title="Acousonde / STP") +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 
```

Temperature drop but no buzz recorded and the depth of the STP tag is deeper than the one provided by the acousonde (time lag?).



## 25 August 07:16

```{r, echo=FALSE}
acou = setDT(buzz)[dateTime %between% c('2016-08-25 06:50:00', 
                                        '2016-08-25 08:50:00')]
st = setDT(stp)[dateTime %between% c('2016-08-25 06:50:00', 
                                     '2016-08-25 08:50:00')]
st[!is.na(st$depth),c(1,5:6,8:11)]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profile on 25th August at 06:50 from the acousonde and depths recorded by the STP in green and buzzes in red."}
ggplot(acou, aes(dateTime, -depth)) +
  geom_path(size=0.1) + 
  geom_point(data=acou[acou$buzz==1,], size=1.5,colour="red",shape=15) +
  geom_point(size=2, data=st, aes(y=-depth, x=dateTime), colour="green") + 
  labs(x="", y="Depth (m)",title="Acousonde / STP mismatch") +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 
```
Drop in temperature associated with a depth recorded at 07:10, which seems to match pretty well buzzes!! Depths recorded by STP seem to match as well depths recorded by the acousonde, suggesting no time lag between both signals.
Keep in mind that NOT ALL temperature drops are plotted here because depth was not always associated with a drop in temperature.


## 25 August 09:53 and 10:03

```{r, echo=FALSE}
acou = setDT(buzz)[dateTime %between% c('2016-08-25 09:50:00', 
                                        '2016-08-25 11:50:00')]
st = setDT(stp)[dateTime %between% c('2016-08-25 09:50:00', 
                                     '2016-08-25 11:50:00')]
st[!is.na(st$depth),c(1,5:6,8:11)]
```


```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profile on 25th August at 09:53 from the acousonde and depths recorded by the STP in green and buzzes in red."}
ggplot(acou, aes(dateTime, -depth)) +
  geom_path(size=0.1) + 
  geom_point(data=acou[acou$buzz==1,], size=1.5,colour="red",shape=15) +
  geom_point(size=2, data=st, aes(y=-depth, x=dateTime), colour="green") + 
  labs(x="", y="Depth (m)",title="Acousonde / STP") +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 
```
2 temperature drops associated with a depth match during a single dive.




## 26 August 03:30, 03:31, 03:58

```{r, echo=FALSE}
acou = setDT(buzz)[dateTime %between% c('2016-08-26 03:15:00', 
                                        '2016-08-26 05:15:00')]
st = setDT(stp)[dateTime %between% c('2016-08-26 03:15:00', 
                                     '2016-08-26 05:15:00')]
st[!is.na(st$depth),c(1,5:6,8:11)]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profile on 26th August at 08:50 from the acousonde and depths recorded by the STP in green and buzzes in red."}
ggplot(acou, aes(dateTime, -depth)) +
  geom_path(size=0.1) + 
  geom_point(data=acou[acou$buzz==1,], size=1.5,colour="red",shape=15) +
  geom_point(size=2, data=st, aes(y=-depth, x=dateTime), colour="green") + 
  labs(x="", y="Depth (m)",title="Acousonde / STP mismatch") +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 
```
2 tempearture drops before the ascent during 2 consecutive dives below 600 m.


## 26 August 14:26

```{r, echo=FALSE}
acou = setDT(buzz)[dateTime %between% c('2016-08-26 14:20:00',
                                        '2016-08-26 15:20:00')]
st = setDT(stp)[dateTime %between% c('2016-08-26 14:20:00', 
                                     '2016-08-26 15:20:00')]
st[!is.na(st$depth),c(1,5:6,8:11)]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profile on 26th August from the acousonde and depths recorded by the STP in green and buzzes in red."}
ggplot(acou, aes(dateTime, -depth)) +
  geom_path(size=0.1) + 
  geom_point(data=acou[acou$buzz==1,], size=1.5,colour="red",shape=15) +
  geom_point(size=2, data=st, aes(y=-depth, x=dateTime), colour="green") + 
  labs(x="", y="Depth (m)",title="Acousonde / STP") +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 
```
2 temperature drops occurred below 300 m during a single dive, and seem associated with buzzes (before and after the drops).


## 26 August 16:57, 16:59

```{r, echo=FALSE}
acou = setDT(buzz)[dateTime %between% c('2016-08-26 16:50:00',
                                        '2016-08-26 17:30:00')]
st = setDT(stp)[dateTime %between% c('2016-08-26 16:50:00', 
                                     '2016-08-26 17:30:00')]
st[!is.na(st$depth),c(1,5:6,8:11)]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profile on 26th August at 16:57 from the acousonde and depths recorded by the STP in green and buzzes in red."}
ggplot(acou, aes(dateTime, -depth)) +
  geom_path(size=0.1) + 
  geom_point(data=acou[acou$buzz==1,], size=1.5,colour="red",shape=15) +
  geom_point(size=2, data=st, aes(y=-depth, x=dateTime), colour="green") + 
  labs(x="", y="Depth (m)",title="Acousonde / STP") +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 
```

No buzz, but one drop in temperature (water ingestion?). Complete mismatch with depth for the 2nd ST record below 60 m, so it might be an error.

One possibility mentionned by Susanna would be to extract the ST directly from the acousonde (coded signals provided by WC). The advantage of this would be to have the exact same time between ST and buzzes, and maybe more accurate STs. 











# Match between buzzes and ST drop {.tabset}

## 25 August 07:16

```{r, echo=FALSE}
acou = setDT(buzz)[dateTime %between% c('2016-08-25 06:30:00', 
                                        '2016-08-25 07:30:00')]
st = setDT(stp)[dateTime %between% c('2016-08-25 06:30:00', 
                                     '2016-08-25 07:30:00')]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profile on 25th August from the acousonde (buzz in red, ST in green) and ST recorded by the STP (bottom)."}
p1 = ggplot(acou, aes(dateTime, -depth)) +
  geom_path(size=0.1) + 
  geom_point(data=acou[acou$buzz==1,], size=1.5,colour="red",shape=15) +
  geom_point(size=2, data=st, aes(y=-depth, x=dateTime), colour="green") + 
  labs(x="", y="Depth (m)",title="Buzzes (red) / STP records (green)") +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,hjust=0.5,angle=90,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.1) + 
  ylim(30,38) +
  geom_point(size=1, aes(y=stp, x=dateTime, colour=type)) + 
  scale_colour_brewer(palette="Set2") +
  labs(x="", y="STP (degrees)",title="STP") +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,hjust=0.5,angle=90,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.position="bottom",
        legend.title = element_blank(),
        legend.key.height = unit(0.2, 'cm'), 
        legend.key.width = unit(0.2, 'cm'),  
        legend.key = element_rect(fill = "transparent", colour = "transparent"),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

grid.arrange(p1,p2)
```



## 25 August 09:53

```{r, echo=FALSE}
acou = setDT(buzz)[dateTime %between% c('2016-08-25 09:45:00', 
                                        '2016-08-25 10:10:00')]
st = setDT(stp)[dateTime %between% c('2016-08-25 09:45:00', 
                                     '2016-08-25 10:10:00')]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profile on 25th August at 09:53 from the acousonde (buzz in red, ST in green) and ST recorded by the STP (bottom)."}
p1 = ggplot(acou, aes(dateTime, -depth)) +
  geom_path(size=0.1) + 
  geom_point(data=acou[acou$buzz==1,], size=1.5,colour="red",shape=15) +
  geom_point(size=2, data=st, aes(y=-depth, x=dateTime), colour="green") + 
  labs(x="", y="Depth (m)",title="Buzzes (red) / STP records (green)") +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,hjust=0.5,angle=90,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.1) + 
  ylim(30,38) +
  geom_point(size=1, aes(y=stp, x=dateTime, colour=type)) +
  scale_colour_brewer(palette="Set2") +
  labs(x="", y="STP (degrees)",title="STP") +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.position="bottom",
        legend.title = element_blank(),
        legend.key.height = unit(0.2, 'cm'), #change legend key height
        legend.key.width = unit(0.2, 'cm'), #change legend key width
        legend.key = element_rect(fill = "transparent", colour = "transparent"),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

grid.arrange(p1,p2)
```



## 26 August 03:30

```{r, echo=FALSE}
acou = setDT(buzz)[dateTime %between% c('2016-08-26 03:15:00', 
                                        '2016-08-26 04:12:00')]
st = setDT(stp)[dateTime %between% c('2016-08-26 03:15:00', 
                                     '2016-08-26 04:12:00')]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profile on 26th August at 03:30 from the acousonde (buzz in red, ST in green) and ST recorded by the STP (bottom)."}
p1 = ggplot(acou, aes(dateTime, -depth)) +
  geom_path(size=0.1) + 
  geom_point(data=acou[acou$buzz==1,], size=1.5,colour="red",shape=15) +
  geom_point(size=2, data=st, aes(y=-depth, x=dateTime), colour="green") + 
  labs(x="", y="Depth (m)",title="Buzzes (red) / STP records (green)") +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,hjust=0.5,angle=90,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.1) + 
  ylim(30,38) +
  geom_point(size=1, aes(y=stp, x=dateTime, colour=type)) + 
  scale_colour_brewer(palette="Set2") +
  labs(x="", y="STP (degrees)",title="STP") +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.position="bottom",
        legend.title = element_blank(),
        legend.key.height = unit(0.2, 'cm'), #change legend key height
        legend.key.width = unit(0.2, 'cm'), #change legend key width
        legend.key = element_rect(fill = "transparent", colour = "transparent"),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

grid.arrange(p1,p2)
```




## 26 August 14:26

```{r, echo=FALSE}
acou = setDT(buzz)[dateTime %between% c('2016-08-26 14:20:00',
                                        '2016-08-26 14:40:00')]
st = setDT(stp)[dateTime %between% c('2016-08-26 14:20:00', 
                                     '2016-08-26 14:40:00')]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profile on 26th August at 14:26 from the acousonde (buzz in red, ST in green) and ST recorded by the STP (bottom)."}
p1 = ggplot(acou, aes(dateTime, -depth)) +
  geom_path(size=0.1) + 
  geom_point(data=acou[acou$buzz==1,], size=1.5,colour="red",shape=15) +
  geom_point(size=2, data=st, aes(y=-depth, x=dateTime), colour="green") + 
  labs(x="", y="Depth (m)",title="Buzzes (red) / STP records (green)") +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,hjust=0.5,angle=90,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.1) + 
  ylim(30,38) +
  geom_point(size=1, aes(y=stp, x=dateTime, colour=type)) + 
  scale_colour_brewer(palette="Set2") +
  labs(x="", y="STP (degrees)",title="STP") +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.position="bottom",
        legend.title = element_blank(),
        legend.key.height = unit(0.2, 'cm'), #change legend key height
        legend.key.width = unit(0.2, 'cm'), #change legend key width
        legend.key = element_rect(fill = "transparent", colour = "transparent"),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

grid.arrange(p1,p2)
```









# Some statistics {.tabset}

## Number of ST drops and time between ST drops
```{r, echo=TRUE}
new = merge(buzz, stp[,c("dateTime","depth","stp","type","water_temp")], 
            by="dateTime",all.x=TRUE)
new = new[!(new$days==1),]  # remove day 1 because no buzz recorded
stp = data.frame(stp)
dat = stp[stp$type=="Feeding starts",]

# number of feeding events per 24h
nrow(dat) / as.numeric(difftime(dat$dateTime[nrow(dat)], dat$dateTime[1], unit="days"))

# Time elapsed between feeding events (in min)
summary(as.numeric(difftime(dat$dateTime[2:nrow(dat)], 
                           dat$dateTime[1:nrow(dat)-1], unit="min")))

# time elapsed between feeding start and feeding ends (in min)
difftime(stp$dateTime[stp$type=="Feeding Ends"], 
         stp$dateTime[stp$type=="Feeding starts"], unit="min")
```


## Time elapsed between ST drops and buzzes
```{r, echo=FALSE}
new   = data.frame(new)
feed  = new[new$type=="Feeding Initial STP" & !is.na(new$type),]
time  = data.frame("event"=0,"dateTime"=0,"time_bef"=NA,"time_aft"=NA,"buzz_dur"=0)
time2 = NULL

for (i in 1:as.numeric(table(new$type)[1])) {
  # select each ST drop
  event   = feed[i,]
  
  # select acousonde records within 5 min before and after ST drop
  bef  = data.frame(setDT(new)[dateTime %between% c(event$dateTime-(60*5),   # 5 minutes before
                                                    event$dateTime)])        # table(bef$buzz)
  aft  = data.frame(setDT(new)[dateTime %between% c(event$dateTime,
                                                    event$dateTime+(60*5))]) # 5 minutes after, table(aft$buzz)
  bef_aft = rbind(bef, aft)
  
  time$event    = i
  time$dateTime = event$dateTime
  time$buzz_dur = nrow(rbind(bef[bef$buzz==1,],aft[aft$buzz==1,]))
  
  # find the closest buzz BEFORE ST drop
  bef$diff = abs(as.numeric(difftime(event$dateTime, 
                                         bef$dateTime[1:nrow(bef)], unit="sec")))
  bef_buzz <- bef[bef$buzz==1,]
  if(nrow(bef_buzz)!=0) {
  time$time_bef = bef_buzz$diff[which.min(bef_buzz$diff)] }
  
  # find the closest buzz AFTER ST drop
  aft$diff = abs(as.numeric(difftime(event$dateTime, 
                                     aft$dateTime[1:nrow(aft)], unit="sec")))
  aft_buzz <- aft[aft$buzz==1,]
  if(nrow(aft_buzz)!=0) {
  time$time_aft = aft_buzz$diff[which.min(aft_buzz$diff)] }
  
  # store result
  time2 = rbind(time2, time) 
}

bef = time2[,c("event","dateTime","time_bef")]
colnames(bef)[3] = "time"
bef$when = "before"
aft = time2[,c("event","dateTime","time_aft")]
colnames(aft)[3] = "time"
aft$when = "after"
time = rbind(bef, aft)  
time$when = as.factor(time$when)
```


```{r, echo=TRUE}
time2
summary(time2)
```


```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Time elapsed between ST drop and buzzes for Eistla."}
ggplot(time, aes(x=when, y=time, fill=when)) +
  geom_boxplot(size=0.1) + 
  geom_point(size=1) + 
  scale_fill_brewer(palette="Set2") +
  labs(x="", y="Time elapsed (sec)") +
  theme(axis.title.y = element_text(size=10,color="black"),
        axis.title.x = element_text(size=10,color="black"),
        axis.text.x  = element_text(size=10,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=10,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.position="none",
        legend.title = element_blank(),
        legend.key.height = unit(0.2, 'cm'), 
        legend.key.width = unit(0.2, 'cm'),
        legend.key = element_rect(fill = "transparent", colour = "transparent"),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 
```
