---
title: "Visual match acousonde-STP for Mara"
author: "Philippine CHAMBAULT"
date: "28/12/2021"
output:
  bookdown::html_document2:
    number_sections: yes
    code_folding: show
    df_print: default
    fig_caption: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = TRUE,
  fig.align = "center",
  message = FALSE,
  warning = FALSE,
  # cache   = FALSE,
  out.width = "100%"
  # comment = NA
)
```

                       

```{r, global_options, include=FALSE}
library(ggplot2)
library(gridExtra)
library(tidyverse)
library(dplyr)
library(viridis)
library(DT)
library(data.table)
Sys.setlocale("LC_TIME", "English")
```





# Import data {.tabset}

## STP 
```{r, echo=TRUE}
stp  <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/MSCA-GF/ANALYSES/Rdata/STP/3.STP_clean_7ids.RDS")
stp = data.frame(stp)
stp = stp[stp$ptt=="7618-Mara",]
DT::datatable(stp[1:30,],options=list(scrollX=T))
table(stp$typ2)

# Duration of the STP
round(difftime(stp$dateTime[nrow(stp)], stp$dateTime[1], units="days")) 
```

## Acousonde
```{r, echo=TRUE}
buzz <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/MSCA-GF/ANALYSES/Rdata/Acou_calib/buzz_Eistla_Frida_Thora_Mara_phases_2m.RDS")
buzz = data.frame(buzz)
buzz = buzz[buzz$id=="Mara",]
DT::datatable(buzz[1:100,],options=list(scrollX=T)) 

# Time elapsed (in days) between release and first buzz:
round(difftime(buzz$dateTime[buzz$buzz==1][[1]], 
               buzz$dateTime[1], units="hours"))

# Duration of the acousonde
round(difftime(buzz$dateTime[nrow(buzz)], buzz$dateTime[1], units="days")) 

# Proportion of phases identified using the diveMove package
table(buzz$phase) / nrow(buzz) * 100
```



# STP over time {.tabset}

## All data included

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Stomach temperature over time and according to event type."}
ggplot(stp, aes(x=dateTime, y=stp)) +
  geom_path(size=0.2,shape=19) +
  geom_point(size=1) +
  geom_point(data=stp[stp$type2=="start",], colour="red",shape=15,size=1) +
        # geom_point(data=stp[stp$type2=="end",], colour="orange",shape=15,size=1) +
  labs(x="", y="STP (degrees)",title="Mara") +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 
```
Some potential outliers below 10 degrees. Let's remove them and see what the curve looks like.

## Without outliers
```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Stomach temperature over time after discarding outliers above 40 and below 10 degrees."}
ggplot(stp[!(stp$stp>40 | stp$stp<10 | is.na(stp$stp)),], aes(x=dateTime, y=stp)) +
  geom_path(size=0.2,shape=19) +
  geom_point(size=1) +
  geom_point(data=stp[stp$type2=="start",], colour="red",shape=15,size=1) +
  labs(x="", y="STP (degrees)",title="Mara") +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 
```




# Temporal overlap

```{r, echo=TRUE}
buzz$type  = "Acousonde"
stp$type   = "STP"
stp = data.frame(stp)
dat = rbind(buzz[,c("dateTime","type")], 
            stp[!is.na(stp$depth),c("dateTime","type")])
dat$type = as.factor(dat$type)
buzz = data.frame(buzz)
b = buzz[buzz$buzz==1,]

# temporal overlap between STP and buzzes
round(difftime(buzz$dateTime[nrow(buzz)], 
               buzz$dateTime[buzz$buzz==1][[1]], units="hours")) 
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Temporal overlap between the STP and the acousonde. Red dots refer to buzzes."}
ggplot(dat, aes(y=dateTime, x=type)) +
  geom_point(size=1.5,colour="black",shape=19) +
  geom_point(data=b,size=1.5,colour="red",shape=19) +
  labs(x="", y="Time",title="Mara") +
  coord_flip() +
  geom_hline(aes(yintercept=as.numeric(b$dateTime[1])), 
             color="blue",linetype=4) +
  geom_hline(aes(yintercept=as.numeric(b$dateTime[nrow(b)])), 
             color="blue",linetype=4) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 
```
Only 1 hour of overlap between the acousonde when buzzes and the STP.






# Correlation between STP and Acousonde {.tabset}

## Before removing outliers
```{r, echo=FALSE}
merge <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/MSCA-GF/ANALYSES/Rdata/merge_depth_STP_Acousonde_Mara.RDS")
summary(merge$stp)
cor.test(merge$depth.y, merge$depth.x)
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Correlation between depth recorded from STP and the ones from the Acousonde from Mara before removing outliers."}
ggplot(merge, aes(depth.x, depth.y)) +
  labs(x="Depth from STP (m)",y="Depth from Acousonde (m)",title="Mara") +
  geom_smooth(method=lm,size=0.6) +
  geom_point(size=1, colour="brown") + 
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 
```

## After removing outliers

```{r, echo=FALSE}
merge = merge[!(merge$stp<10 | merge$stp>40),]
summary(merge$stp)
cor.test(merge$depth.y, merge$depth.x)
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Correlation between depth recorded from STP and the ones from the Acousonde from Mara after removing outliers."}
ggplot(merge, aes(depth.x, depth.y)) +
  labs(x="Depth from STP (m)",y="Depth from Acousonde (m)",title="Mara") +
  geom_smooth(method=lm,size=0.6) +
  geom_point(size=1, colour="brown") + 
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 
```














# Match between buzzes and ST drop {.tabset}

## 11 August 16:30

```{r, echo=FALSE}
acou = setDT(buzz)[dateTime %between% c('2014-08-11 16:00:00',
                                        '2014-08-11 17:00:00')]
st = setDT(stp)[dateTime %between% c('2014-08-11 16:00:00', 
                                     '2014-08-11 17:00:00')]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profile from the acousonde (buzz in green, ST start in red, ST end in orange) and ST recorded by the STP (bottom)."}
p1 = ggplot(acou, aes(dateTime, -depth)) +
  geom_path(size=0.1) + 
  geom_point(data=acou[acou$buzz==1,], size=1.5,colour="green",shape=17) +
  geom_point(size=2, data=st, aes(y=-depth, x=dateTime), colour="red", pch=15) + 
  labs(x="", y="Depth (m)",title="Buzzes (green) / STP records (red)") +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,hjust=0.5,angle=90,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.1) + 
  # ylim(30,38) +
  geom_point(size=1, aes(y=stp, x=dateTime)) + 
  geom_point(data=st[st$type2=="start",], colour="red",shape=15,size=3) +
  geom_point(data=st[st$type2=="end",], colour="orange",shape=15,size=3) +
  labs(x="", y="STP (degrees)",title="STP") +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.position="bottom",
        legend.title = element_blank(),
        legend.key.height = unit(0.2, 'cm'), #change legend key height
        legend.key.width = unit(0.2, 'cm'), #change legend key width
        legend.key = element_rect(fill = "transparent", colour = "transparent"),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

grid.arrange(p1,p2)
```







## 11 August 17:30

```{r, echo=FALSE}
acou = setDT(buzz)[dateTime %between% c('2014-08-11 17:30:00',
                                        '2014-08-11 19:00:00')]
st = setDT(stp)[dateTime %between% c('2014-08-11 17:30:00', 
                                     '2014-08-11 19:00:00')]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profile from the acousonde (buzz in green, ST start in red, ST end in orange) and ST recorded by the STP (bottom)."}
p1 = ggplot(acou, aes(dateTime, -depth)) +
  geom_path(size=0.1) + 
  geom_point(data=acou[acou$buzz==1,], size=1.5,colour="green",shape=17) +
  geom_point(size=2, data=st, aes(y=-depth, x=dateTime), colour="red", pch=15) + 
  labs(x="", y="Depth (m)",title="Buzzes (green) / STP records (red)") +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,hjust=0.5,angle=90,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.1) + 
  # ylim(30,38) +
  geom_point(size=1, aes(y=stp, x=dateTime)) + 
  geom_point(data=st[st$type2=="start",], colour="red",shape=15,size=3) +
  geom_point(data=st[st$type2=="end",], colour="orange",shape=15,size=3) +
  labs(x="", y="STP (degrees)",title="STP") +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.position="bottom",
        legend.title = element_blank(),
        legend.key.height = unit(0.2, 'cm'), #change legend key height
        legend.key.width = unit(0.2, 'cm'), #change legend key width
        legend.key = element_rect(fill = "transparent", colour = "transparent"),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

grid.arrange(p1,p2)
```



## 11 August 20:00

```{r, echo=FALSE}
acou = setDT(buzz)[dateTime %between% c('2014-08-11 20:30:00',
                                        '2014-08-11 21:30:00')]
st = setDT(stp)[dateTime %between% c('2014-08-11 20:30:00', 
                                     '2014-08-11 21:30:00')]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profile from the acousonde (buzz in green, ST start in red, ST end in orange) and ST recorded by the STP (bottom)."}
p1 = ggplot(acou, aes(dateTime, -depth)) +
  geom_path(size=0.1) + 
  geom_point(data=acou[acou$buzz==1,], size=1.5,colour="green",shape=17) +
  geom_point(size=2, data=st, aes(y=-depth, x=dateTime), colour="red", pch=15) + 
  labs(x="", y="Depth (m)",title="Buzzes (green) / STP records (red)") +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,hjust=0.5,angle=90,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.1) + 
  # ylim(30,38) +
  geom_point(size=1, aes(y=stp, x=dateTime)) + 
  geom_point(data=st[st$type2=="start",], colour="red",shape=15,size=3) +
  geom_point(data=st[st$type2=="end",], colour="orange",shape=15,size=3) +
  labs(x="", y="STP (degrees)",title="STP") +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.position="bottom",
        legend.title = element_blank(),
        legend.key.height = unit(0.2, 'cm'), #change legend key height
        legend.key.width = unit(0.2, 'cm'), #change legend key width
        legend.key = element_rect(fill = "transparent", colour = "transparent"),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

grid.arrange(p1,p2)
```


## 12 August 00:40

```{r, echo=FALSE}
buzz = data.frame(buzz)
head(buzz[buzz$buzz==1,])
acou = setDT(buzz)[dateTime %between% c('2014-08-12 00:40:00',
                                        '2014-08-12 02:30:00')]
st = setDT(stp)[dateTime %between% c('2014-08-12 00:40:00', 
                                     '2014-08-12 02:30:00')]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profile from the acousonde (buzz in green, ST start in red, ST end in orange) and ST recorded by the STP (bottom)."}
p1 = ggplot(acou, aes(dateTime, -depth)) +
  geom_path(size=0.1) + 
  geom_point(data=acou[acou$buzz==1,], size=1.5,colour="green",shape=17) +
  geom_point(size=2, data=st, aes(y=-depth, x=dateTime), colour="red", pch=15) + 
  labs(x="", y="Depth (m)",title="Buzzes (green) / STP records (red)") +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,hjust=0.5,angle=90,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.1) + 
  # ylim(30,38) +
  geom_point(size=1, aes(y=stp, x=dateTime)) + 
  geom_point(data=st[st$type2=="start",], colour="red",shape=15,size=3) +
  geom_point(data=st[st$type2=="end",], colour="orange",shape=15,size=3) +
  labs(x="", y="STP (degrees)",title="STP") +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.position="bottom",
        legend.title = element_blank(),
        legend.key.height = unit(0.2, 'cm'), #change legend key height
        legend.key.width = unit(0.2, 'cm'), #change legend key width
        legend.key = element_rect(fill = "transparent", colour = "transparent"),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

grid.arrange(p1,p2)
```



## 12 August 04:30

```{r, echo=FALSE}
acou = setDT(buzz)[dateTime %between% c('2014-08-12 05:20:00',
                                        '2014-08-12 06:30:00')]
st = setDT(stp)[dateTime %between% c('2014-08-12 04:20:00', 
                                     '2014-08-12 06:30:00')]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth profile from the acousonde (buzz in green, ST start in red, ST end in orange) and ST recorded by the STP (bottom)."}
p1 = ggplot(acou, aes(dateTime, -depth)) +
  geom_path(size=0.1) + 
  geom_point(data=acou[acou$buzz==1,], size=1.5,colour="green",shape=17) +
  geom_point(size=2, data=st, aes(y=-depth, x=dateTime), colour="red", pch=15) + 
  labs(x="", y="Depth (m)",title="Buzzes (green) / STP records (red)") +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,hjust=0.5,angle=90,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.title = element_blank(),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.1) + 
  # ylim(30,38) +
  geom_point(size=1, aes(y=stp, x=dateTime)) + 
  geom_point(data=st[st$type2=="start",], colour="red",shape=15,size=3) +
  geom_point(data=st[st$type2=="end",], colour="orange",shape=15,size=3) +
  labs(x="", y="STP (degrees)",title="STP") +
  theme(axis.title.y = element_text(size=8,color="black"),
        axis.title.x = element_text(size=8,color="black"),
        axis.text.x  = element_text(size=8,vjust=0.5,angle=0,color="black"),
        axis.text.y  = element_text(size=8,color="black"),
        panel.background = element_blank(),
        legend.text=element_text(size=10),
        legend.position="bottom",
        legend.title = element_blank(),
        legend.key.height = unit(0.2, 'cm'), #change legend key height
        legend.key.width = unit(0.2, 'cm'), #change legend key width
        legend.key = element_rect(fill = "transparent", colour = "transparent"),
        text=element_text(size=10, family="serif"),
        title = element_text(size=10, face='bold'),
        panel.grid.major = element_line(colour="lightgrey", size=0.1),
        plot.margin = unit(c(0.2,0.2,0.2,0.1), "cm")) 

grid.arrange(p1,p2)
```

No acousonde anymore!!