---
title: "Merge HR to LR (#3965)"
author: "Philippine CHAMBAULT"
date: "18/12/2021"
output:
  bookdown::html_document2:
    number_sections: yes
    code_folding: show
    df_print: default
    fig_caption: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = TRUE,
  fig.align = "center",
  message = FALSE,
  warning = FALSE,
  # cache   = FALSE,
  out.width = "100%"
  # comment = NA
)
```

                       

```{r, global_options, include=FALSE}
library(ggplot2)
library(tidyquant)
library(gridExtra)
library(tidyverse)
library(dplyr)
library(viridis)
library(DT)
library(data.table)
Sys.setlocale("LC_TIME", "English")
```


Objective:

- Compare the high resolution to the low resolution data for this individual (after start and end of each event has been identified).




# Import data {.tabset}

## High resolution
```{r, echo=TRUE}
hr  <- readRDS("./Rdata/STP/3.STP_HR_clean_events_3965.rds")
DT::datatable(hr[1:30,],options=list(scrollX=T))
hr = data.frame(hr)
# number of records
nrow(hr)
# Duration of the tag
round(difftime(hr$dateTime[nrow(hr)], hr$dateTime[1], units="days")) 
# number of ST drops (when a drop >= 1 deg/min)
table(hr$type2)
# range values for STP: 
summary(hr$stp)

# import events summary from LR
event <- readRDS("./Rdata/STP/3.Events_start_stop_3965-HR.rds")
event$dur_class = cut(event$duration, breaks=seq(0, max(event$duration), by=10)) #c(seq(0, 20, by=5), 

phase = event[,c("phase_start","phase_end","duration")] %>%
  group_by(phase_start) %>%
  summarise(nrow=n())
phase$prop = (phase$nrow / nrow(event)) * 100
```


## STP Low resolution
```{r, echo=TRUE}
lr <- readRDS("./Rdata/STP/3.STP_3965-TDR_events_clean.rds")
DT::datatable(lr[1:30,],options=list(scrollX=T))
lr = data.frame(lr)
# number of records
nrow(lr)
# number of ST drops 
table(lr$type2)
# Duration of the tag
round(difftime(lr$dateTime[nrow(lr)], lr$dateTime[1], units="days")) 
# range values for STP: removed outliers < 10 and > 38 deg
summary(lr$stp)
```









# TDR overlaid on STP based on my method {.tabset}
Red dots refer to the feeding start and orange dots to feeding end.

## 2013-08-13 20:43

```{r, echo=FALSE}
start = hr$dateTime[which(hr$type2=="start")[1]] - 60*5
end   = hr$dateTime[which(hr$type2=="end")[1]] + 60*5
st    = setDT(hr)[dateTime %between% c(start,end)]
st    = data.frame(st)

low = setDT(lr)[dateTime %between% c(start, end)]
low = data.frame(low)
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth (top) and STP profiles (bottom) on 2013-08-13 20:43. Red dots feeding start and orange dots feeding end."}
p1 = ggplot(st, aes(dateTime, -depth.x)) +
  geom_path(size=0.1) +
  geom_point(size=0.5, aes(colour=phase), shape=19) +
  scale_color_brewer(palette="Set2") +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="Depth (m)",title=paste0("TDR, ", low$dateTime[1])) +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme_tq() +
  theme(legend.position="none",
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=90,color="black"))

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.2) +
  # ylim(30,37) +
  geom_line(size=0.8, data=low, colour="blue") +
  geom_point(size=0.2) +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="STP (degrees)",title="STP High (black) & low (blue) resolutions") +
  theme_tq() +
  theme(panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=90,color="black"))

grid.arrange(p1,p2)
```



## 2013-08-13 23:36

```{r, echo=FALSE}
start = hr$dateTime[which(hr$type2=="start")[2]] - 60*5
end   = hr$dateTime[which(hr$type2=="end")[2]] + 60*5
st    = setDT(hr)[dateTime %between% c(start,end)]
st    = data.frame(st)
low = setDT(lr)[dateTime %between% c(start, end)]
low = data.frame(low)
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth (top) and STP profiles (bottom) on 2013-08-13 23:36. Red dots are feeding start and orange dots feeding end."}
p1 = ggplot(st, aes(dateTime, -depth.x)) +
  geom_path(size=0.1) +
  geom_point(size=0.5, aes(colour=phase), shape=19) +
  scale_color_brewer(palette="Set2") +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="Depth (m)",title=paste0("TDR, ", low$dateTime[1])) +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme_tq() +
  theme(legend.position="none",
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=90,color="black"))

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.2) +
  # ylim(30,37) +
  geom_line(size=0.8, data=low, colour="blue") +
  geom_point(size=0.2) +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="STP (degrees)",title="STP High (black) & low (blue) resolutions") +
  theme_tq() +
  theme(panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=90,color="black"))

grid.arrange(p1,p2)
```


## 2013-08-14 01:15

```{r, echo=FALSE}
start = hr$dateTime[which(hr$type2=="start")[3]] - 60*5
end   = hr$dateTime[which(hr$type2=="end")[3]] + 60*5
st    = setDT(hr)[dateTime %between% c(start,end)]
st    = data.frame(st)
low = setDT(lr)[dateTime %between% c(start, end)]
low = data.frame(low)
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth (top) and STP profiles (bottom). Red dots are feeding start and orange dots feeding end."}
p1 = ggplot(st, aes(dateTime, -depth.x)) +
  geom_path(size=0.1) +
  geom_point(size=0.5, aes(colour=phase), shape=19) +
  scale_color_brewer(palette="Set2") +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="Depth (m)",title=paste0("TDR, ", low$dateTime[1])) +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme_tq() +
  theme(legend.position="none",
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=90,color="black"))

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.2) +
  # ylim(30,37) +
  geom_line(size=0.8, data=low, colour="blue") +
  geom_point(size=0.2) +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="STP (degrees)",title="STP High (black) & low (blue) resolutions") +
  theme_tq() +
  theme(panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=90,color="black"))

grid.arrange(p1,p2)
```



## 2013-08-14 08:50

```{r, echo=FALSE}
start = hr$dateTime[which(hr$type2=="start")[9]] - 60*5
end   = hr$dateTime[which(hr$type2=="end")[9]] + 60*5
st    = setDT(hr)[dateTime %between% c(start,end)]
st    = data.frame(st)
low = setDT(lr)[dateTime %between% c(start, end)]
low = data.frame(low)
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth (top) and STP profiles (bottom). Red dots are feeding start and orange dots feeding end."}
p1 = ggplot(st, aes(dateTime, -depth.x)) +
  geom_path(size=0.1) +
  geom_point(size=0.5, aes(colour=phase), shape=19) +
  scale_color_brewer(palette="Set2") +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="Depth (m)",title=paste0("TDR, ", low$dateTime[1])) +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme_tq() +
  theme(legend.position="none",
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=90,color="black"))

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.2) +
  # ylim(30,37) +
  geom_line(size=0.8, data=low, colour="blue") +
  geom_point(size=0.2) +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="STP (degrees)",title="STP High (black) & low (blue) resolutions") +
  theme_tq() +
  theme(panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=90,color="black"))

grid.arrange(p1,p2)
```



## 2013-08-14 09:21

```{r, echo=FALSE}
start = hr$dateTime[which(hr$type2=="start")[10]] - 60*5
end   = hr$dateTime[which(hr$type2=="end")[10]] + 60*5
st    = setDT(hr)[dateTime %between% c(start,end)]
st    = data.frame(st)
low = setDT(lr)[dateTime %between% c(start, end)]
low = data.frame(low)
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth (top) and STP profiles (bottom). Red dots are feeding start and orange dots feeding end."}
p1 = ggplot(st, aes(dateTime, -depth.x)) +
  geom_path(size=0.1) +
  geom_point(size=0.5, aes(colour=phase), shape=19) +
  scale_color_brewer(palette="Set2") +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="Depth (m)",title=paste0("TDR, ", low$dateTime[1])) +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme_tq() +
  theme(legend.position="none",
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=90,color="black"))

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.2) +
  # ylim(30,37) +
  geom_line(size=0.8, data=low, colour="blue") +
  geom_point(size=0.2) +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="STP (degrees)",title="STP High (black) & low (blue) resolutions") +
  theme_tq() +
  theme(panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=90,color="black"))

grid.arrange(p1,p2)
```




## 2013-08-15 03:07

```{r, echo=FALSE}
start = hr$dateTime[which(hr$type2=="start")[20]] - 60*5
end   = hr$dateTime[which(hr$type2=="end")[20]] + 60*40
st    = setDT(hr)[dateTime %between% c(start,end)]
st    = data.frame(st)
low = setDT(lr)[dateTime %between% c(start, end)]
low = data.frame(low)
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth (top) and STP profiles (bottom). Red dots are feeding start and orange dots feeding end."}
p1 = ggplot(st, aes(dateTime, -depth.x)) +
  geom_path(size=0.1) +
  geom_point(size=0.5, aes(colour=phase), shape=19) +
  scale_color_brewer(palette="Set2") +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="Depth (m)",title=paste0("TDR, ", low$dateTime[1])) +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme_tq() +
  theme(legend.position="none",
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=90,color="black"))

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.2) +
  # ylim(30,37) +
  geom_line(size=0.8, data=low, colour="blue") +
  geom_point(size=0.2) +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="STP (degrees)",title="STP High (black) & low (blue) resolutions") +
  theme_tq() +
  theme(panel.grid.minor = element_blank())

grid.arrange(p1,p2)
```





## 2013-08-15 15:43

```{r, echo=FALSE}
start = hr$dateTime[which(hr$type2=="start")[30]] - 60*5
end   = hr$dateTime[which(hr$type2=="end")[30]] + 60*40
st    = setDT(hr)[dateTime %between% c(start,end)]
st    = data.frame(st)
low   = setDT(lr)[dateTime %between% c(start, end)]
low   = data.frame(low)
low$dateTime[1]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth (top) and STP profiles (bottom). Red dots are feeding start and orange dots feeding end."}
p1 = ggplot(st, aes(dateTime, -depth.x)) +
  geom_path(size=0.1) +
  geom_point(size=0.5, aes(colour=phase), shape=19) +
  scale_color_brewer(palette="Set2") +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="Depth (m)",title=paste0("TDR, ", low$dateTime[1])) +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme_tq() +
  theme(legend.position="none",
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=45,color="black"))

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.2) +
  ylim(30,37) +
  geom_line(size=0.8, data=low, colour="blue") +
  geom_point(size=0.2) +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="STP (degrees)",title="STP High & low (blue) resolutions") +
  theme_tq() +
  theme(panel.grid.minor = element_blank())

grid.arrange(p1,p2)
```


## 2013-08-16 06:21

```{r, echo=FALSE}
start = hr$dateTime[which(hr$type2=="start")[40]] - 60*5
end   = hr$dateTime[which(hr$type2=="end")[40]] + 60*40
st    = setDT(hr)[dateTime %between% c(start,end)]
st    = data.frame(st)
low   = setDT(lr)[dateTime %between% c(start, end)]
low   = data.frame(low)
low$dateTime[1]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth (top) and STP profiles (bottom). Red dots are feeding start and orange dots feeding end."}
p1 = ggplot(st, aes(dateTime, -depth.x)) +
  geom_path(size=0.1) +
  geom_point(size=0.5, aes(colour=phase), shape=19) +
  scale_color_brewer(palette="Set2") +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="Depth (m)",title=paste0("TDR, ", low$dateTime[1])) +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme_tq() +
  theme(legend.position="none",
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=45,color="black"))

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.2) +
  ylim(30,37) +
  geom_line(size=0.8, data=low, colour="blue") +
  geom_point(size=0.2) +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="STP (degrees)",title="STP High & low (blue) resolutions") +
  theme_tq() +
  theme(panel.grid.minor = element_blank())

grid.arrange(p1,p2)
```


## 2013-08-16 23:58

```{r, echo=FALSE}
start = hr$dateTime[which(hr$type2=="start")[50]] - 60*5
end   = hr$dateTime[which(hr$type2=="end")[50]] + 60*40
st    = setDT(hr)[dateTime %between% c(start,end)]
st    = data.frame(st)
low   = setDT(lr)[dateTime %between% c(start, end)]
low   = data.frame(low)
low$dateTime[1]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth (top) and STP profiles (bottom). Red dots are feeding start and orange dots feeding end."}
p1 = ggplot(st, aes(dateTime, -depth.x)) +
  geom_path(size=0.1) +
  geom_point(size=0.5, aes(colour=phase), shape=19) +
  scale_color_brewer(palette="Set2") +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="Depth (m)",title=paste0("TDR, ", low$dateTime[1])) +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme_tq() +
  theme(legend.position="none",
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=45,color="black"))

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.2) +
  ylim(30,37) +
  geom_line(size=0.8, data=low, colour="blue") +
  geom_point(size=0.2) +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="STP (degrees)",title="STP High & low (blue) resolutions") +
  theme_tq() +
  theme(panel.grid.minor = element_blank())

grid.arrange(p1,p2)
```



## 2013-08-18 06:13

```{r, echo=FALSE}
start = hr$dateTime[which(hr$type2=="start")[60]] - 60*5
end   = hr$dateTime[which(hr$type2=="end")[60]] + 60*40
st    = setDT(hr)[dateTime %between% c(start,end)]
st    = data.frame(st)
low   = setDT(lr)[dateTime %between% c(start, end)]
low   = data.frame(low)
low$dateTime[1]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth (top) and STP profiles (bottom). Red dots are feeding start and orange dots feeding end."}
p1 = ggplot(st, aes(dateTime, -depth.x)) +
  geom_path(size=0.1) +
  geom_point(size=0.5, aes(colour=phase), shape=19) +
  scale_color_brewer(palette="Set2") +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="Depth (m)",title=paste0("TDR, ", low$dateTime[1])) +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme_tq() +
  theme(legend.position="none",
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=45,color="black"))

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.2) +
  ylim(30,37) +
  geom_line(size=0.8, data=low, colour="blue") +
  geom_point(size=0.2) +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="STP (degrees)",title="STP High & low (blue) resolutions") +
  theme_tq() +
  theme(panel.grid.minor = element_blank())

grid.arrange(p1,p2)
```



## 2013-08-10 04:29

```{r, echo=FALSE}
start = hr$dateTime[which(hr$type2=="start")[70]] - 60*5
end   = hr$dateTime[which(hr$type2=="end")[70]] + 60*40
st    = setDT(hr)[dateTime %between% c(start,end)]
st    = data.frame(st)
low   = setDT(lr)[dateTime %between% c(start, end)]
low   = data.frame(low)
low$dateTime[1]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth (top) and STP profiles (bottom). Red dots are feeding start and orange dots feeding end."}
p1 = ggplot(st, aes(dateTime, -depth.x)) +
  geom_path(size=0.1) +
  geom_point(size=0.5, aes(colour=phase), shape=19) +
  scale_color_brewer(palette="Set2") +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="Depth (m)",title=paste0("TDR, ", low$dateTime[1])) +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme_tq() +
  theme(legend.position="none",
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=45,color="black"))

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.2) +
  ylim(30,37) +
  geom_line(size=0.8, data=low, colour="blue") +
  geom_point(size=0.2) +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="STP (degrees)",title="STP High & low (blue) resolutions") +
  theme_tq() +
  theme(panel.grid.minor = element_blank())

grid.arrange(p1,p2)
```



## 2013-08-20 00:18

```{r, echo=FALSE}
start = hr$dateTime[which(hr$type2=="start")[80]] - 60*5
end   = hr$dateTime[which(hr$type2=="end")[80]] + 60*40
st    = setDT(hr)[dateTime %between% c(start,end)]
st    = data.frame(st)
low   = setDT(lr)[dateTime %between% c(start, end)]
low   = data.frame(low)
low$dateTime[1]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth (top) and STP profiles (bottom). Red dots are feeding start and orange dots feeding end."}
p1 = ggplot(st, aes(dateTime, -depth.x)) +
  geom_path(size=0.1) +
  geom_point(size=0.5, aes(colour=phase), shape=19) +
  scale_color_brewer(palette="Set2") +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="Depth (m)",title=paste0("TDR, ", low$dateTime[1])) +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme_tq() +
  theme(legend.position="none",
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=45,color="black"))

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.2) +
  ylim(30,37) +
  geom_line(size=0.8, data=low, colour="blue") +
  geom_point(size=0.2) +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="STP (degrees)",title="STP High & low (blue) resolutions") +
  theme_tq() +
  theme(panel.grid.minor = element_blank())

grid.arrange(p1,p2)
```



## 2013-08-21 01:47

```{r, echo=FALSE}
start = hr$dateTime[which(hr$type2=="start")[90]] - 60*5
end   = hr$dateTime[which(hr$type2=="end")[90]] + 60*40
st    = setDT(hr)[dateTime %between% c(start,end)]
st    = data.frame(st)
low   = setDT(lr)[dateTime %between% c(start, end)]
low   = data.frame(low)
low$dateTime[1]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth (top) and STP profiles (bottom). Red dots are feeding start and orange dots feeding end."}
p1 = ggplot(st, aes(dateTime, -depth.x)) +
  geom_path(size=0.1) +
  geom_point(size=0.5, aes(colour=phase), shape=19) +
  scale_color_brewer(palette="Set2") +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="Depth (m)",title=paste0("TDR, ", low$dateTime[1])) +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme_tq() +
  theme(legend.position="none",
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=45,color="black"))

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.2) +
  ylim(30,37) +
  geom_line(size=0.8, data=low, colour="blue") +
  geom_point(size=0.2) +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="STP (degrees)",title="STP High & low (blue) resolutions") +
  theme_tq() +
  theme(panel.grid.minor = element_blank())

grid.arrange(p1,p2)
```



## 2013-08-21 08:04

```{r, echo=FALSE}
start = hr$dateTime[which(hr$type2=="start")[94]] - 60*30
end   = hr$dateTime[which(hr$type2=="end")[94]] + 60*40
st    = setDT(hr)[dateTime %between% c(start,end)]
st    = data.frame(st)
low   = setDT(lr)[dateTime %between% c(start, end)]
low   = data.frame(low)
low$dateTime[1]
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Depth (top) and STP profiles (bottom). Red dots are feeding start and orange dots feeding end."}
p1 = ggplot(st, aes(dateTime, -depth.x)) +
  geom_path(size=0.1) +
  geom_point(size=0.5, aes(colour=phase), shape=19) +
  scale_color_brewer(palette="Set2") +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="Depth (m)",title=paste0("TDR, ", low$dateTime[1])) +
  geom_hline(yintercept=0,linetype=2, color="blue", size=0.3) +
  theme_tq() +
  theme(legend.position="none",
        panel.grid.minor = element_blank(),
        axis.text.y = element_text(size=8,vjust=0.5,angle=45,color="black"))

p2 = ggplot(st[!is.na(st$stp),], aes(dateTime, stp)) +
  geom_path(size=0.2) +
  ylim(30,37) +
  geom_line(size=0.8, data=low, colour="blue") +
  geom_point(size=0.2) +
  geom_point(size=3, data=st[st$type2=="start",], colour="red", shape=15) +
  geom_point(size=3, data=st[st$type2=="end",], colour="orange", shape=15) +
  labs(x="", y="STP (degrees)",title="STP High & low (blue) resolutions") +
  theme_tq() +
  theme(panel.grid.minor = element_blank())

grid.arrange(p1,p2)
```





# Duration of feeding events  {.tabset}

## Histo of duration

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the ST drops duration (in min)."}
ggplot(event, aes(duration)) +
  geom_histogram(binwidth=5,color="black", fill="lightgrey") + 
  labs(y="Frequency", x="ST drops duration (min)") +
  theme_tq()
```
Feeding events last between 3 and 50 min (mean: 14.8 min, SD: 8.6 min).

## According to dive phase
```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the ST drop duration (min) acording to dive phase, e.g. D: Descent, A: Ascent, B: Bottom, X: Surface."}
ggplot(event, aes(duration)) +
  geom_histogram(binwidth=10, color="black", aes(fill=phase_start)) + 
  labs(y="Frequency", x="ST drops duration (min)") +
  facet_wrap(.~phase_start) +
  theme_tq() +
  scale_fill_brewer(palette="Set1") +
  theme(legend.position = "none")
```

Longer events at the bottom (phase _B_, mean: 18.7 min), but also long events close to the surface (phase _X_, mean: 16 min).






# Depth of feeding events {.tabset}

## Depth at ST drops (from HR data)

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the depth (from LR data) of ST drops (m)."}
ggplot(event, aes(-dep_start)) +
  geom_histogram(binwidth=20,color="black", fill="lightgrey") + 
  labs(y="Frequency", x="ST drops depth (m)") +
  coord_flip() +
  theme_tq()
```


## According to duration

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the depth of ST drops (m)."}
ggplot(event, aes(-dep_start)) +
  geom_histogram(binwidth=10, color="black", aes(fill=dur_class)) + 
  labs(y="Frequency", x="ST drops depth (m)") +
  coord_flip() +
  theme_tq()
```

## Depth at ST drops according to dive phase

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the depth of ST drops (m)."}
ggplot(event, aes(-dep_start)) +
  geom_histogram(binwidth=10, color="black", aes(fill=phase_start)) + 
  labs(y="Frequency", x="ST drops depth (m)") +
  coord_flip() +
  theme_tq()
```




# Dive phase frequency {.tabset}

## Summary
```{r, echo=FALSE}
# Compute the position of labels
data <- phase %>% 
  arrange(desc(phase_start)) %>%
  mutate(prop = prop) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )
data$prop = round(data$prop)

kruskal.test(duration~phase_start, event)
event %>%
  group_by(phase_start) %>%
  summarise(mean=mean(duration),
            sd=sd(duration),
            min=min(duration),
            max=max(duration))
```
 
## Pie chart
```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the depth of ST drops (m)."}
ggplot(data, aes(x="", y=prop, fill=phase_start)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  theme_void() +
  geom_text(aes(y=ypos, label=paste0(prop,"%")), color="white", size=6) +
  scale_fill_brewer(palette="Set1")
```
A majority of ST drops during the Bottom (_B_, 37%), Ascent (_A_, 26%) and Descent (_D_, 22%). 15% of the events occurred at the surface (_X_), might be some water ingestion.




