---
title: "Buzzes and drops (Eistla, Thora, Mara)"
author: "Philippine CHAMBAULT"
date: "30/12/2021"
output:
  bookdown::html_document2:
    number_sections: yes
    code_folding: show
    df_print: default
    fig_caption: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = TRUE,
  fig.align = "center",
  message = FALSE,
  warning = FALSE,
  # cache   = FALSE,
  out.width = "100%"
  # comment = NA
)
```

                       

```{r, global_options, include=FALSE}
library(ggplot2)
library(tidyquant)
library(gridExtra)
library(tidyverse)
library(dplyr)
library(viridis)
library(DT)
library(data.table)
Sys.setlocale("LC_TIME", "English")
```


Objectives:

- Estimate the number of dives with buzzes

- Estimate the number of dives with ST drops

- Calculate the proportion of successful (dives with both buzz and drop) vs. unsuccessful dives.




# Import data (1 row=1 dive)

```{r, echo=F}
dive3  <- readRDS("./Rdata/STP/4.Dive_summary_drop_buzz_clean_Eistla_Thora_Frida_Mara.rds")
DT::datatable(dive3[1:30,],options=list(scrollX=T))
dive3 = dive3[,-c(20:21)]
colnames(dive3)[2] = "ptt"
dive3 = data.frame(dive3)
# number of dives per ID
table(dive3$ptt)
nrow(dive3[dive3$maxdep<5,]) / nrow(dive3) * 100
```





# Instrumention effect {.tabset}

```{r, echo=T}
acou <- readRDS("./Rdata/STP/4.STP_Acou_mergeAll_Eistla_Thora_Frida_Mara.rds")
time = acou %>%
  group_by(ptt) %>%
  summarise("release_day"=head(dateTime,1),
            "day_first_buzz"=head(dateTime[buzz!=0],1),
            "day_first_drop"=head(dateTime[type2=="start" & !is.na(type2)],1))
```

## Duration between release and first buzz
```{r, echo=F}
time$time_first_buzz = as.numeric(difftime(time$day_first_buzz, 
                                           time$release_day, units="hours"))
time[,c(1,5)]
```
The first buzzes after release occured between 9h (Mara) and 27h (Frida) after instrumentation.



## Duration between release and first drop
```{r, echo=F}
time$time_first_drop = as.numeric(difftime(time$day_first_drop, time$release_day, 
                                           units="hours"))
time[,c(1,6)]
```
Some drops occurred way before the first buzzes (at least for Mara and Thora < 1h after release).





# Drops characteristics (on the 7 ids) {.tabset}

## Drop duration
```{r, echo=F}
event <- readRDS("./Rdata/STP/3.Events_start_stop_7ids.rds")
event = data.frame(event)
event %>%
  group_by(ptt) %>%
  summarise(mean=mean(dur, na.rm=T),
            sd=sd(dur, na.rm=T),
            max=max(dur, na.rm=T))
```
```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the mean drop duration per individual."}
ggplot(event, aes(dur)) +
  geom_histogram(binwidth=5,color="black", fill="lightgrey") + 
  labs(y="Counts", x="Mean drop duration (min)") +
  facet_wrap(.~ptt, scales="free_y") +
  theme_tq()
```


## Drop depth
```{r, echo=F}
event %>%
  group_by(ptt) %>%
  summarise(mean=mean(depth, na.rm=T),
            sd=sd(depth, na.rm=T),
            min=min(depth, na.rm=T),
            max=max(depth, na.rm=T))
```
Some drops very close to the surface (especially for #7617-15 and #7618-15). Might be water ingestion, need to be removed. Very few depths for #Eistla, #7617-15 and #7618-15.

```{r}
nrow(event[event$depth<=5,c("ptt","start","end","dur","depth")])
```
223 dives shallower than 5 m that should be removed.



```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the mean dive depth per individual during ST drops (derived from STP)."}
ggplot(event, aes(-depth)) +
  geom_histogram(binwidth=20,color="black", fill="lightgrey") + 
  labs(y="N dive with drop", x="Mean dive depth (m)") +
  facet_wrap(.~ptt, scales="free_x") +
  coord_flip() +
  theme_tq()
```


## Inter-drop duration (in hour)

```{r, echo=F}
event %>%
  group_by(ptt) %>%
  summarise(mean=mean(dur_nofeed/60, na.rm=T),
            sd=sd(dur_nofeed/60, na.rm=T),
            min=min(dur_nofeed/60, na.rm=T),
            max=max(dur_nofeed/60, na.rm=T))
```


```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Boxplot of the inter-drop duration (in hours) per individual."}
ggplot(event, aes(x=ptt, y=dur_nofeed/60)) +
  geom_boxplot(aes(fill=ptt)) + 
  labs(x="PTT", y="Inter-drop duration (h)") +
  scale_fill_tq() +
  theme_tq() +
  # ylim(0,80) +
  theme(legend.position="none")
```









# Buzzes and drops {.tabset}

## Histogram of mean depth

```{r, echo=F}
sum2 = dive3 %>%
  group_by(ptt) %>%
  summarise(tot_dive=n(),
            tot_buzz=sum(buzz),
            buzz_dive=mean(buzz),
            dives_buzz=sum(buzz!=0),
            max_buzz_dive=max(buzz),
            tot_drop=sum(drop, na.rm=T),
            drop_dive=mean(drop, na.rm=T),
            unsuccessful=sum(buzz>=1 & drop==0),
            successful=sum(buzz>=1 & drop!=0))
sum2 = data.frame(sum2)
sum2$prop_buzz       = sum2$dives_buzz / sum2$tot_dive * 100
sum2$prop_unsuccess  = sum2$unsuccessful / sum2$dives_buzz * 100
sum2$prop_success    = sum2$successful / sum2$dives_buzz * 100
sum2
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the mean dive depth  (derived from acousonde) per individual according to the number of drop per dive."}
ggplot(dive3, aes(-meandep)) + #, fill=as.factor(drop)
  geom_histogram(binwidth=10, position="dodge") + 
  labs(y="N dive", x="Mean dive depth (m)") +
  facet_grid(drop~ptt, scales="free_x") +
  coord_flip() +
  theme_tq() +
  scale_fill_tq() +
  theme(legend.position="none")
```
Dives including 1 drop occur mainly below 200 m for both individuals, although a very few dives with drops occurred close to the surface as well. One dive including 2 drops was performed by Eistla.



## Proportion of dives with buzzes

```{r, echo=F}
sum = data.frame("ptt"=c("Eistla","Eistla","Frida","Frida",
                         "Mara","Mara","Thora","Thora"),
                 "buzz"=c(0,1,0,1,0,1,0,1),
                 "dives"=c(sum2$tot_dive[1]-sum2$dives_buzz[1],sum2$dives_buzz[1],
                           sum2$tot_dive[2]-sum2$dives_buzz[2],sum2$dives_buzz[2],
                           sum2$tot_dive[3]-sum2$dives_buzz[3],sum2$dives_buzz[3],
                           sum2$tot_dive[4]-sum2$dives_buzz[4],sum2$dives_buzz[4]))
sum$prop[sum$ptt=="Eistla"] = sum$dives[sum$ptt=="Eistla"] / sum2$tot_dive[1] * 100
sum$prop[sum$ptt=="Thora"]  = sum$dives[sum$ptt=="Thora"] / sum2$tot_dive[4] * 100
sum$prop[sum$ptt=="Mara"] = sum$dives[sum$ptt=="Mara"] / sum2$tot_dive[3] * 100
sum$prop[sum$ptt=="Frida"] = sum$dives[sum$ptt=="Frida"] / sum2$tot_dive[2] * 100

sum$buzz = as.factor(sum$buzz)
sum
```


```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the number of dives with buzzes."}
ggplot(sum, aes(x=ptt, y=prop, fill=buzz)) +
  geom_bar(stat="identity", position="fill") + 
  labs(y="Frequency", x="PTT") +
  theme_tq() +
  scale_fill_tq() 
```
27% of the dives with buzzes for Eistla, 11% for Frida, 4% for Mara and 20% for Thora.



## Proportion of dives with drops

```{r, echo=F}
sum = data.frame("ptt"=c("Eistla","Eistla","Frida","Frida",
                         "Mara","Mara","Thora","Thora"),
                 "drop"=c(0,1,0,1,0,1,0,1),
                 "dives"=c(sum2$tot_dive[1]-sum2$tot_drop[1],sum2$tot_drop[1],
                           sum2$tot_dive[2]-sum2$tot_drop[2],sum2$tot_drop[2],
                           sum2$tot_dive[3]-sum2$tot_drop[3],sum2$tot_drop[3],
                           sum2$tot_dive[4]-sum2$tot_drop[4],sum2$tot_drop[4]))
sum$prop[sum$ptt=="Eistla"] = sum$dives[sum$ptt=="Eistla"] / sum2$tot_dive[1] * 100
sum$prop[sum$ptt=="Frida"]  = sum$dives[sum$ptt=="Frida"] / sum2$tot_dive[2] * 100
sum$prop[sum$ptt=="Mara"]  = sum$dives[sum$ptt=="Mara"] / sum2$tot_dive[3] * 100
sum$prop[sum$ptt=="Thora"]  = sum$dives[sum$ptt=="Thora"] / sum2$tot_dive[4] * 100
sum$drop = as.factor(sum$drop)
sum
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the proportion of dives with drops."}
ggplot(sum, aes(x=ptt, y=prop, fill=drop)) +
  geom_bar(stat="identity", position="fill") + 
  labs(y="Frequency", x="PTT") +
  theme_tq() +
  scale_fill_tq() 
```
Among the total number of dives per individual, less than 1% contained ST drops except for Mara (8%). This number is very low, either indicative of a low level of feeding during summer, but also of a technical issue with the STP missing some events.




## Number of buzz per dive

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Boxplot of the number of buzz per dive."}
ggplot(dive3, aes(x=ptt, y=buzz, fill=ptt)) +
  geom_boxplot() +
  labs(y="Number of buzzes", x="PTT") +
  theme_tq() +
  scale_fill_tq() +
  theme(legend.position="none")
```
Up to 36 and 101 buzzes were recorded during a single dive for Eistla and Thora (only 8/dive tops for Mara), respectively. But on average, the 4 females performed between 0.8 (Mara) and 4.5 (Eistla) buzzes per dive. Should remove the first hours after capture (before the first buzz to be more realistic).



```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the mean number of buzzes per dive."}
ggplot(sum2, aes(x=ptt, y=buzz_dive, fill=ptt)) +
  geom_bar(stat="identity") + 
  labs(y="Average number of buzzes/dive", x="PTT") +
  geom_text(aes(label=signif(buzz_dive,2)), vjust=0, size=4) +
  theme_tq() +
  scale_fill_tq() +
  theme(legend.position="none")
```



## Number of drop per dive

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Histogram of the mean number of drop per dive."}
ggplot(sum2, aes(x=ptt, y=drop_dive, fill=ptt)) +
  geom_bar(stat="identity") + 
  labs(y="Number of drops/dive", x="PTT") +
  geom_text(aes(label=signif(drop_dive,2)), vjust=0, size=4) +
  theme_tq() +
  scale_fill_tq() +
  theme(legend.position="none")
```


## Successful vs. unsuccessful dives

```{r, echo=F}
sum2[,c("ptt","prop_unsuccess","prop_success")]
```
Very low values: between 2.9 and 5.7 % of the dives appear successful, except the higher proportion for Mara (20%) but likely be due to the very low number of drop during dives with buzzes (only an hour of match between the acousonde and the STP). Despite the high temporal resolution of the STP (every 2 minutes when no drop and every 1 min during drop), some data gaps suggest the tag might have missed some events. This hypothesis is reinforced by the high resolution data collected from #3965 from which the tag was retrieved and recorded nearly three times more events (12/day) vs. less than 5/day for Eistla and Thora. Could also be due to a strong inter-individual heterogeneity.




## Dives with drops but no buzz

```{r, echo=F}
nrow(dive3[dive3$buzz==0 & dive3$drop!=0,])  # 20 dives
dive3[dive3$buzz==0 & dive3$drop!=0,c("ptt","dive","maxdep","dur")]
summary(dive3$maxdep[dive3$buzz==0 & dive3$drop!=0])
```
20 dives in total contained a drop but no buzz. Some of these dives (n=6) were shallow (<65 m), and could be therefore associated with water ingestion rather than prey ingestion, especially the one occurring at 5 m due to the very short duration of the event (<1 min), but some others were deep and possibly real prey catches.













# Duration between drop and buzz {.tabset}

## Buzz before drop

```{r, echo=F}
dive3 %>%
  group_by(ptt) %>%
  summarise(mean=mean(dur_bef_drop, na.rm=T),
            sd=sd(dur_bef_drop, na.rm=T),
            max=max(dur_bef_drop, na.rm=T),
            min=min(dur_bef_drop, na.rm=T))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Boxplot of the time elapsed (in sec) between drop and the buzz before drop."}
ggplot(dive3, aes(x=ptt, y=dur_bef_drop, fill=ptt)) +
  geom_boxplot() +
  labs(y="Duration (sec)", x="PTT") +
  theme_tq() +
  scale_fill_tq() +
  theme(legend.position="none")
```
The average duration between a buzz and the next drop is 27 (sd: 24) and 38 (sd: 28) sec for Eistla and Thora, respectively. The maximum duration is 54 sec for Eistla and 79 sec for Thora, and the minimum duration is 2 sec for both narwhals.





## Buzz after drop

```{r, echo=F}
dive3 %>%
  group_by(ptt) %>%
  summarise(mean=mean(dur_aft_drop, na.rm=T),
            sd=sd(dur_aft_drop, na.rm=T),
            max=max(dur_aft_drop, na.rm=T),
            min=min(dur_aft_drop, na.rm=T))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Boxplot of the time elapsed (in sec) between drop and the buzz after drop."}
ggplot(dive3, aes(x=ptt, y=dur_aft_drop, fill=ptt)) +
  geom_boxplot() +
  labs(y="Duration (sec)", x="PTT") +
  theme_tq() +
  ylim(0,100) +
  scale_fill_tq() +
  theme(legend.position="none")
```

The average duration between a drop and the next buzz is 28 (sd: 36) and 16 (sd: 18) sec for Eistla and Thora, respectively. The maximum duration is 82 sec for Eistla and 51 sec for Thora, and the minimum duration is 1 sec for both narwhals.









# Number of buzzes during dives with drop {.tabset}

## Buzz before drop

```{r, echo=F}
dive3[dive3$drop!=0,] %>%
  group_by(ptt) %>%
  summarise(mean=mean(Nbuzz_bef, na.rm=T),
            sd=sd(Nbuzz_bef, na.rm=T),
            max=max(Nbuzz_bef, na.rm=T),
            min=min(Nbuzz_bef, na.rm=T))
```


## Buzz after drop

```{r, echo=F}
dive3[dive3$drop!=0,] %>%
  group_by(ptt) %>%
  summarise(mean=mean(Nbuzz_aft, na.rm=T),
            sd=sd(Nbuzz_aft, na.rm=T),
            max=max(Nbuzz_aft, na.rm=T),
            min=min(Nbuzz_aft, na.rm=T))
```







# Correlation between buzzes and drop {.tabset}

## Dive duration & N buzzes

```{r, echo=F}
cor.test(dive3$buzz, dive3$dur) 
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Relationship between dive duration (min) and the number of buzzes during dives with drop"}
ggplot(dive3, aes(buzz, dur)) +
  labs(x="N buzzes during dive",y="Dive duration (min)") +
  geom_smooth(method='gam',size=0.6) +
  facet_wrap(.~ptt, scales="free_x") +
  geom_point(size=1, colour="brown") +
  scale_fill_tq() +
  theme_tq() 
```



## Drop & buzzes

```{r, echo=F}
cor.test(dive3$buzz, dive3$drop) 
```


## Drop depth & drop duration

```{r, echo=F}
cor.test(dive3$dep_drop, dive3$drop_dur) 
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Relationship between drop duration (min) and drop depth."}
ggplot(dive3, aes(dep_drop, drop_dur, colour=ptt)) +
  labs(x="Drop depth (m)",y="Drop duration (min)") +
  geom_smooth(method='lm',size=0.6) +
  geom_point(size=1) +
  scale_fill_tq() +
  theme_tq() 
```



## Drop depth & dive duration

```{r, echo=F}
cor.test(dive3$dep_drop, dive3$dur) 
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4, fig.cap="Relationship between drop duration (min) and dive duration (min)."}
ggplot(dive3, aes(dep_drop, dur, colour=ptt)) +
  labs(x="Drop depth (m)",y="Dive duration (min)") +
  geom_smooth(method='lm',size=0.6) +
  geom_point(size=1) +
  scale_fill_tq() +
  theme_tq() 
```


